Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/metis-language-and-proofs.tex
Fixed table.

The \TPTP language is the input language to encode problems used by \Metis.
It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
The \TPTP syntax describes a well-defined grammar to handle annotated
formulas with the following form:

\begin{verbatim}
  language(name, role, formula).,
\end{verbatim}

where the \name{language} can be \name{fof} or \name{cnf}. The \name{name}
serves to identify the formula within the problem. Each formula
assumes a \name{role}, this could be an \name{axiom},
\name{conjecture}, \name{definition}, \name{plain} or an \name{hypothesis}.
The formulas include the constants \verb!$true! and \verb!$false!, negation
unary operator (\verb!~!), and the binary connectives (\verb!&!, \verb!|!,
\verb!=>!, \verb!<=>!) to represent $⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$,
and $⇔$ respectively.

\begin{myexamplenum}
For instance, let us express the problem
$p\, ⊢ ¬  (p ∧ ¬ p) ∨ (q ∧ ¬ q)$
in \TPTP syntax. We begin by declaring the $p$ axiom using the \verb!axiom!
keyword. Later, we include the expected conclusion using the
\verb!conjecture! keyword.

\begin{verbatim}
  fof(h, axiom, p).
  fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
\end{verbatim}

\end{myexamplenum}

>>>>

The \TPTP language is the input language to encode problems used by \Metis.
It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
The \TPTP syntax describes a well-defined grammar to handle annotated
formulas with the following form:
\begin{verbatim}
  language(name, role, formula).,
\end{verbatim}
where the \name{language} can be \name{fof} or \name{cnf}. The
\name{name} serves to identify the formula within the problem. Each
formula assumes a \name{role}, this could be an \name{axiom},
\name{conjecture}, \name{definition}, \name{plain} or an
\name{hypothesis}.  The formulas include the constants
\verb!$true! and \verb!$false!, the negation unary operator~\verb!~!,
and the binary connectives \verb!&!, \verb!|!, \verb!=>!, and
\verb!<=>! to represent $⊤$, $⊥$, $¬$, $∧$, $∨$, $⇒$, and $⇔$
respectively.

\begin{myexamplenum}
  For instance, let us express the problem
  $p\, ⊢ ¬ (p ∧ ¬ p) ∨ (q ∧ ¬ q)$ in \TPTP syntax. We begin by
  declaring the $p$ axiom using the \verb!axiom!  keyword. Next, we
  include the expected conclusion using the \verb!conjecture! keyword.
\begin{verbatim}
  fof(h, axiom, p).
  fof(goal, conjecture, ~ ((p & ~ p) | (q & ~ q))).
\end{verbatim}
\end{myexamplenum}
